 % Project description
\def\projectdescription{
	Model predictive control (MPC) has gained more attention in the past years as it is a powerful modern control technique that relies on repeatedly solving an open-loop optimal control problem. In order to obtain high-quality optimal input signals, an accurate prediction model is required, which is often unavailable or difficult to identify. In recent years data-driven control approaches have become more interesting because they use only measured data to control unknown systems without prior model identification. A major issue in data-driven control is the treatment of measurement noise, which in recent publications is treated to be deterministically bounded \cite{Berberich_2021}.  However, this assumption does not generally hold for a real system. Alternatively, a stochastic model can be used to model the state transition function as in \cite{kamthe2018}. However, there is a lack of theoretical guarantees of probabilistic models, e.g., Gaussian processes.
	
	The goal of this thesis is to implement a probabilistic MPC scheme relying on Gaussian process models to represent the transition function of a discrete-time system with noisy measurements and uncertainty models. The thesis proves that one probabilistic GP-MPC algorithm is enough for both linear and nonlinear models. A common challenge is that most data-driven approaches require numerous interactions with the environment. However, conducting a vast number of interactions can often be unfeasible in real-world scenarios, especially in fields like robotics\cite{marc2015robotics}. The proposed GP-MPC model is capable of controlling any system with a small number of interactions, which increases the data efficiency even in an uncertainty model.  
	
	% Within the scope of the work, a literature review on Gaussian processes and probabilistic MPC will first be conducted. Then, the method should will be implemented and tested in simulation. If this was successful, the algorithm should be tested on a real plant. Finally, the experimental data will be evaluated and the results obtained will be discussed. 
}

 % Project tasks
\def\tasks{
\begin{packedenumerate}
	\item Literature review
	\item Familiarization with Gaussian processes and MPC 
        \item To learn a probabilistic transition model using Gaussian Processes (GPs) to incorporate model uncertainty into long-term predictions
	\item Implementation of the probabilistic MPC algorithm
        \item Implementation of GP-MPC on linear and nonlinear dynamics.
	\item Comparison to other MPC algorithms/implementations
	\item Testing in simulation and, if successful, testing on a real plant(optional)
	\item Evaluation and discussion
\end{packedenumerate}
}
